---
output:
  github_document:
    html_preview: TRUE
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  warning = FALSE
)
```
## Overview

The goal of this `"binomial"` [R](http://www.r-project.org/) package is to provide functions for computing binomial distribution measures and probabilites.

-  `bin_choose()` using factorial to caculate the number combinations in which successes an occur in trials.

-  `bin_probability()` it takes three arguemnts sucess, trials, and prob to calculate bionomial probability of success in a given trial and given probability.

-  `bin_distribution()` it takes two aruments trials & prob to calculate the probability distribution of success in a given trial and given probability. Returns a `"bindis"` object which is a `data.frame`.

-  `bin_distribution()` it takes two aruments trials & prob and calculates the cumulated probability of each trial. Returns a `"bincum"` object which is a `data.frame`.

-  `plot()` method for a `"bindis"` or `"bincum"` object to plot the distribution.

-  `bin_variable()` it takes two aruments trials & prob and calculates an object of class caled "binvar" which is a binomial random variable object and creates a binomial variable object of class `"binvar"`

-  `summary()` method for a `"binvar"` object.


Given number of trials and probability of success:

-  `bin_mean()` computes the mean.
-  `bin_variance()` computes the variance.
-  `bin_mode()` computes the mode.
-  `bin_skewness()` computes the skewness.
-  `bin_kurtosis()` computes the kurtosis.

## Motivation

This package has been developed to illustrate some of the concepts behind the creation of an R package.

## Installation

Install the development version from GitHub via the package `"devtools"`:

```r
# development version from GitHub:
#install.packages("devtools") 

# install "binomial" (without vignettes)
devtools::install_github("/stat133-sp19/hw-stat133-AziziDunia/binomial")

# install "binomial" (with vignettes)
devtools::install_github("/stat133-sp19/hw-stat133-AziziDunia/binomial", build_vignettes = TRUE)
```

## Usage

```{r}
#call the binomial pacakge with library()
library(binomial)

# binomial random variable
bin_var <- bin_variable(trials = 7,prob = 0.2)
bin_var

# binomial probability
bin_prb <- bin_probability(success = 4, trials = 7, prob = 0.2)
bin_prb

# binomial distribution
bin_dist <- bin_distribution(trials = 7, prob = 0.2)
bin_dist

# plotting binomial ditribution
plot(bin_dist)

# binomial cumulative distribution
bin_cum <- bin_cumulative(7, 0.2)
bin_cum 

# plotting binomial cumulative distribution
plot(bin_cum )

# binomial random variable summary statistics
summary(bin_var)

# summary measures
bin_mean(2, 0.2)
bin_variance(2, 0.2)
bin_mode(2, 0.2)
bin_skewnees(2, 0.2)
bin_kurtosis(2, 0.2)
```

