---
title: "Introduction-to-Binomial"
author: "Dunia Azizi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction-to-Binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", warning = FALSE)
library(binomial)
```

## Binomial Distribution

Under certain conditions, a random variable that represents the number of successes in a series of trials has a probability distribution is called the **binomial distribution** . The `"binomial"` package is a self-created package which includes functions that calculates probability of binomial random variable and its related properties such as mean, variance, mode, skewness, and kurtosis of binomial distribution. The `"binomial"` package has main functions that the user is expected to invoke and methods that support classes of objects generated by some of the main functions. Examples are provided below. 

## Conditions

The **binomial distribution** describes the behavior of a count variable \(X\) if the following conditions apply:

1: The number of observations n is fixed.

2: Each observation is independent.

3: Each observation represents one of two outcomes
("success" or "failure").

4: The probability of "success" p is the same for each outcome.

## Main functions of binomial distribution package
1) Calculate the number of different combinations when given certain number of trials and successes. For example, we play a game 7 times and expect 4 successes with k = successes and n = number of trials 
```{r}
bin_choose(n=7,k=4)
```

2) Find the bionomial probability when given certain number of trials and successes. For example, calculate the probability of winning 4 times in 7 trials with success probability of 0.2 for each single trial.
```{r}
bin_probability(success = 4, trials = 7, prob = 0.2)
```

3) Find the binomial probability distribution when given certain number of trials and successes. Obtain a dataframe where the function outputs a table with 'Success' as the first column and 'Probability' as the second.
```{r}
bin_dist <- bin_distribution(trials = 7, prob = 0.2)
bin_dist
```

To plot the dataframe, call `plot()` on the distribution table
```{r}
plot(bin_dist)
```

4) Find the cumulative probability distribution of the above example
```{r}
bin_cum <- bin_cumulative(7, 0.2)
bin_cum 
```

To plot the cumulative probability distribution, call `plot()`.
```{r}
plot(bin_cum)
```

5) Create binomial random variable the example above
```{r}
bin_var <- bin_variable(trials = 7,prob = 0.2)
bin_var
```

To obtain a summary of the binomial variable, call `summary()`.
```{r}
bin_sum <- summary(bin_var)
bin_sum
```
##Functions of measures

###Mean   

To find the expected value of \(X\), use the `bin_mean()` function.
```{r}
bin_mean(2, 0.2)
```  

### Variance

To find the variance of \(X\), use the `bin_variance()` function.
```{r}
bin_variance(2, 0.2)
```

### Mode  

The most likely number of success in 2 independent trials with 0.2 probability of success on each trial can be found with `bin_mode()`.
```{r}
bin_mode(2, 0.2)
```


### Skewness  

Skewness is a measure of the asymmetry of the probability distribution of a random variable about its mean. The skewness value can be position, negative, or undefined. To find the skewness of a binomial random variable, use the `bin_skewness()` function.
```{r}
bin_skewnees(2, 0.2)
```  

### Kurtosis  

The Kurtosis is a measure of the "tailedness" of the probability distribution of a random variable. Kurtosis is a descriptor of the shape of a probability distribution. To find the kurtosis of a binomial random variable, use the `bin_kurtosis()` function.
```{r}
bin_kurtosis(2, 0.2)
```
